Recursive properties of branching and BGG resolution

### 2011-02-10 AffineLieAlgebras/MQFT2010/article.tex
arXiv version (1102.1702v1) added, Russian translation for TMPh started

%\usepackage{ucs}
%\usepackage{pb-diagram}
%\usepackage{epstopdf}
%\usepackage{verbatim}
%\newenvironment{comment}
%{\par\noindent{\bf TODO}\\}
%{\\\hfill$\scriptstyle\blacksquare$\par}

@@

%TCIDATA{OutputFilter=Latex.dll}
%TCIDATA{LastRevised=Wed Dec 15 21:36:06 2010}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{CSTFile=article.cst}

\newtheorem{statement}{Statement}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}{Lemma}
\newtheorem{mynote}{Note}[section]
%\newtheorem{proof}{Proof}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
%\input{tcilatex}

@@

\title{Recursive properties of branching and Weyl-Verma formulas}
\author{V D Lyakhovsky$^1$ and A A Nazarov$^2$}

@@

\begin{abstract}
Recurrent relations for branching coefficients are based on a special type of
singular element decomposition. We show that this decomposition can be used to
construct the parabolic Verma modules and finally to obtain the generalized
Weyl-Verma formulas for characters.
These Weyl-Verma formulas explicitly exhibit how branching and the generalized
BGG-resolution properties are connected.
\end{abstract}

@@

The resolution of the irreducible modules in terms of infinite-dimensional ones is important for the
theory of integrable spin chains \cite{derk1008}. In the Baxter $\mathcal{Q}$-operator approach the generic transfer
matrices corresponding to the (generalized) Verma modules are factorized into the product of Baxter
operator. Then the resolution allows to calculate the transfer matrices for finite-dimensional
auxiliary spaces.

To show the connection of the BGG resolution with the branching we use the recursive approach presented in \cite
{2010arXiv1007.0318L} (similar to the one used in \cite{ilyin812pbc} for
maximal embeddings). We consider the subalgebra $\af$ together with its
counterpart $\afb$ ''orthogonal'' to $\af$ with respect to
the Killing form and also $\widetilde{\afb}:=\afb\oplus \frak{h}_{\perp }$ where $\frak{h}=\frak{\frak{h}_{\af}}\oplus
\frak{h}_{\afb}\oplus \frak{h}_{\perp }$. For any reductive
algebra $\af$ the subalgebra $\afb\hookrightarrow \gf$
is regular and reductive. For a highest weight integrable module $%
L^{\left(\mu \right) }$ and orthogonal subalgebra $\af_{\bot }$ we
consider the singular element $\Psi ^{\left( \mu \right) }$ (the numerator
in the Weyl character formula $ch\left( L^{\mu }\right) =\frac{\Psi ^{\left(
\mu \right) }}{\Psi ^{\left( 0\right) }}$, see for example \cite
{humphreys1997introduction}) the Weyl denominator $\Psi _{\af_{\bot
}}^{\left( 0\right) }$ for the orthogonal subalgebra and the projection $%
\Psi _{\left( \af,\af_{\bot }\right) }^{\left( \mu \right) }=\pi _{%
\af}\frac{\Psi _{\gf}^{\left( \mu \right) }}{\Psi _{\af_{\bot
}}^{\left( 0\right) }}$. It is shown that the element $\Psi _{\gf%
}^{\left( \mu \right) }$ can be decomposed into a combination of Weyl
numerators $\Psi _{\af_{\bot }}^{\left( \nu \right) }$ with $\nu \in P_{%
\mathfrak{a}_{\bot}}^{+}$. This decomposition provides the possibility to
construct the set of highest weight modules $L_{\widetilde{\afb}%
}^{\mu _{\widetilde{\afb}}}$. When the injection \ $\af%
_{\bot }\hookrightarrow \gf$ \ satisfies the ''standard parabolic''
conditions these modules give rise to the parabolic Verma modules $M_{\left(
\widetilde{\afb}\hookrightarrow \gf\right) }^{\mu _{%
\widetilde{\afb}}}$ so that the initial character $ch\left(
L^{\mu }\right) $ is finally decomposed into the alternating sum of such. On
the other hand when the parabolic conditions are violated the construction
survives and exhibits a decomposition with respect to a set of Verma
modules $M_{\left( \widetilde{\frak{b}_{\perp }},\gf\right) }^{\mu _{%
\widetilde{\afb}}}$. In such a situation the algebra $%
\widetilde{\frak{b}_{\perp }}$ is not a subalgebra in $\gf$ but a
contraction of $\widetilde{\afb}$.

Some general properties of the proposed decompositions are formulated in
terms of a specific element $\Gamma _{\af\rightarrow \gf}$ of the
group algebra $\mathcal{E}\left( \gf\right) $ called ''the injection
fan''. Using this tool the simple and explicit algorithm for branching
coefficients computations applicable for an arbitrary (maximal or
nonmaximal) subalgebras of finite-dimensional or affine Lie algebras was
obtained in \cite{2010arXiv1007.0318L}.

Possible further developments are presented in Section \ref{sec:conclusions}.

@@

Consider Lie algebras (affine Lie algebras) $\gf$ and $\af$ and an
injection $\af\hookrightarrow \gf$ such that $\af$ is a
reductive subalgebra $\frak{a\subset g}$ with correlated root spaces: $\frak{%
h}_{\af}^{\ast }\subset \frak{h}_{\gf}^{\ast }$. We use the
following notations:

$\frak{g=n}^{-}+\frak{b}+\frak{n}^{+}$ --- the Cartan decomposition;

$r$ , $\left( r_{\af}\right) $ --- the rank of the algebra $\gf$ $%
\left( \mathrm{{resp. }\af}\right) $ ;

$\Delta $ $\left( \Delta _{\af}\right) $--- the root system; $\Delta
^{+} $ $\left( \mathrm{{resp. }\Delta _{\af}^{+}}\right) $--- the
positive root system (of $\gf$ and $\af$ respectively);

$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\af}\left(
\alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $%
\Delta $ (resp. in $\left( \Delta _{\af}\right) $);

$S\quad \left( S_{\af}\right) $ --- the system of simple roots (of $%
\gf$ and $\af$ respectively);

$\alpha _{i}$ , $\left( \alpha _{\left( \af\right) j}\right) $ --- the $%
i$-th (resp. $j$-th) basic root for $\gf$ $\left( \mathrm{{resp.}\frak{a%
}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\af}\right) $;

$\delta $ --- the imaginary root of $\gf$ (and of $\af$ if any);

$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \af\right) j}^{\vee
}\right) $--- the basic coroot for $\gf$ $\left( \mathrm{{resp.}\af%
}\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\af}\right) $;

$W$ , $\left( W_{\af}\right) $--- the corresponding Weyl group;

$C$ , $\left( C_{\af}\right) $--- the fundamental Weyl chamber;

$\bar{C}, \left(\bar{C_{\af}}\right)$ --- the closure of the
fundamental Weyl chamber;

@@

$\rho $\ , $\left( \rho _{\af}\right) $\ --- the Weyl vector;

$L^{\mu }$\ $\left( L_{\af}^{\nu }\right) $\ --- the integrable module
of $\gf$ with the highest weight $\mu $\ ; (resp. integrable $\af$
-module with the highest weight $\nu $ );

$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\af}^{\nu }\right) $ ---
the weight diagram of $L^{\mu }$ (resp. ${}L_{\af}^{\nu }$ );

$P$ (resp. $P_{\af} $) \ --- the weight lattice;

$P^{+}$ (resp. $P_{\af}^{+} $) \ --- the dominant weight lattice;

$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\xi }^{\left( \nu \right)
}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mathrm{{%
resp. }\in P_{\af}}\right) $ in the module $L^{\mu }$ , (resp. $\xi \in
L_{\af}^{\nu } $);

$ch\left( L^{\mu }\right) $ (resp. $\mathrm{ch}\left( L_{\af}^{\nu
}\right) $)--- the formal character of $L^{\mu }$ (resp. $L_{\af}^{\nu
} $);

@@

$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
mult}\left( \alpha \right) }}\quad $ (resp. $R_{\af}:=\prod_{\alpha \in
\Delta _{\af}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\af%
}\left( \alpha \right) } $)--- the Weyl denominator.

\section{Orthogonal subalgebra and singular elements}

@@

In this section we shall show how the recurrent approach to branching
problem leads naturally to a presentation of the formal character in terms
of parabolic (generalized) Verma modules. Consider a reductive Lie algebra $%
\gf$ and its reductive subalgebra $\af\subset \gf$. Let $%
L^{\mu} $ be the highest weight integrable module of $\gf$, $\mu \in
P^{+}$. Let $L^{\mu }$ be completely reducible with respect to $\af$,
\begin{equation*}
L_{\gf\downarrow \af}^{\mu }=\bigoplus\limits_{\nu \in P_{\af%
}^{+}}b_{\nu }^{\left( \mu \right) }L_{\af}^{\nu }.
\end{equation*}
Using the projection operator $\pi _{\af}$ (to the weight space $\frak{%
h_{a}}^{\ast }$) one can rewrite this decomposition in terms of formal
characters:
\begin{equation}
\pi _{\af}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\af%
}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\af}^{\nu }\right) .
\label{branching1}
\end{equation}
The module $L^{\mu }$ has the BGG-resolution (see \cite
{bernstein1976category,bernstein1975differential,bernstein1971structure} and
\cite{humphreys2008representations}). All the members of the filtration
sequence are the direct sums of Verma modules and all their highest weights $%
\nu $ are strongly linked to $\mu $:
\begin{equation*}
\left\{ \nu \right\} =\left\{ w\left( \mu +\rho \right) -\rho |w\in
W\right\} .
\end{equation*}

@@

Let $\frak{h}_{\af}$ be a Cartan subalgebra of $\mathfrak{g}$. For $%
\mathfrak{a}\hookrightarrow \gf$ introduce the ''orthogonal partner'' $%
\mathfrak{a}_{\bot }\hookrightarrow \gf$ .

Consider the root subspace $\frak{h}_{\perp \af}^{\ast }$ orthogonal to
$\af$,
\begin{equation*}
\frak{h}_{\perp \af}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
h\in \frak{h}_{\af};\eta \left( h\right) =0\right\} ,
\end{equation*}
and the roots (correspondingly -- positive roots) of $\gf$ orthogonal
to $\af$,
\begin{eqnarray}
\Delta _{\afb} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
h\in \frak{h}_{\af};\beta \left( h\right) =0\right\} ,
\label{delta a ort} \\
\Delta _{\afb}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
}^{+}|\forall h\in \frak{h}_{\af};\beta ^{+}\left( h\right) =0\right\} .
\notag
\end{eqnarray}
Let $W_{\afb}$ be the subgroup of $W$ generated by the
reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\afb}^{+}$ . The subsystem $\Delta _{\afb}$ determines the
subalgebra $\afb$ with the Cartan subalgebra $\frak{h}_{\af%
_{\perp }}$. Let
\begin{equation*}
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \af}^{\ast
}|\forall h\in \frak{h}_{\af\oplus \afb};\eta \left(
h\right) =0\right\}
\end{equation*}
so that $\gf$ has the subalgebras
\begin{eqnarray*}
\widetilde{\afb} &:&=\afb\oplus \frak{h}_{\perp }
\\
\widetilde{\af} &:&=\af\oplus \frak{h}_{\perp }.
\end{eqnarray*}
Notice that $\mathfrak{a} \oplus \mathfrak{a}_{\bot}$ in general is not a
subalgebra of $\mathfrak{g}$

For the Cartan subalgebras we have the decomposition
\begin{equation}
\frak{h}=\frak{\frak{h}_{\af}}\oplus \frak{h}_{\afb}\oplus
\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\af}}}\oplus \frak{h}_{%
\afb}=\frak{\frak{h}_{\widetilde{\afb}}}\oplus
\frak{h}_{\af}.
\end{equation}
For the subalgebras $\af$ and $\afb$ consider the
corresponding Weyl vectors, $\rho _{\af}$ and $\rho _{\afb} $ . Form the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
D}_{\afb}$ of the injection:
\begin{equation}
\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho ,
\end{equation}
\begin{equation}
\mathcal{D}_{\afb}:=\rho _{\afb}-\pi _{\af%
_{\perp }}\rho .  \label{defect ort}
\end{equation}

For the highest weight $\mu \in P^{+}$ consider the linked weights $\left\{
\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections to
$h_{\afb}^{\ast }$ additionally shifted by the defect $-%
\mathcal{D}_{\afb}$:
\begin{equation*}
\mu _{\afb}\left( w\right) :=\pi _{\afb}\left[
w(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad w\in W.
\end{equation*}
For $\mu \in P^{+}$ among the weights $\left\{ \mu _{\afb}\left( w\right) |w\in W\right\} $ one can always choose those located in
the fundamental chamber $\overline{C_{\afb}}$. Let $U$ be the
set of representatives $u$ for the classes $W/W_{\afb}$ such
that

\begin{equation}
U:=\left\{ u\in W|\quad \mu _{\afb}\left( u\right) \in
\overline{C_{\afb}}\right\} \quad .  \label{U-def}
\end{equation}
Thus we can select the following subsets:
\begin{equation}
\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\af%
_{\perp }},\quad u\in U,  \label{mu-a}
\end{equation}
and
\begin{equation}
\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[
u(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad u\in U.
\label{mu-a-tilda}
\end{equation}

Note that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
since it is built on the roots of the algebra $\mathfrak{g}$.

For the modules we are interested in the Weyl-Kac formula for $\mathrm{ch}%
\left( L^{\mu }\right) $ can be written in terms of singular elements \cite
{humphreys1997introduction}
\begin{equation*}
\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w(\mu +\rho
)-\rho },
\end{equation*}
namely,
\begin{equation}
\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi
^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
\label{Weyl-Kac2}
\end{equation}
The same is true for the submodules $\mathrm{ch}\left( L_{\af}^{\nu
}\right) $ in (\ref{branching1})
\begin{equation*}
\mathrm{ch}\left( L_{\af}^{\nu }\right) =\frac{\Psi _{\af}^{\left(
\nu \right) }}{\Psi _{\af}^{\left( 0\right) }}=\frac{\Psi _{\af%
}^{\left( \nu \right) }}{R_{\af}},
\end{equation*}
with
\begin{equation*}
\Psi _{\af}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\af%
}}\epsilon (w)e^{w(\nu +\rho _{_{\af}})-\rho _{_{\af}}}.
\end{equation*}

>>>>

@@

\newtheorem{statement}{Statement}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}{Lemma}
\newtheorem{mynote}{Note}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
%\input{tcilatex}

@@

\title{Recursive properties of branching and BGG resolution}
\author{V D Lyakhovsky$^1$ and A A Nazarov$^{2,3}$\\
{\small $^1$ Theoretical Department, SPb State University}\\
{\small 198904, Sankt-Petersburg, Russia}\\
{\small e-mail: lyakh1507@nm.ru}\\
{\small $^2$ Theoretical Department, SPb State University}\\
{\small 198904, Sankt-Petersburg, Russia}\\
{\small$^{3}$ Chebyshev Laboratory,}\\
{\small Department of Mathematics and Mechanics, SPb State University}\\
{\small 199178, Saint-Petersburg, Russia}\\
{\small email: antonnaz@gmail.com}}

@@

\begin{abstract}
Recurrent relations for branching coefficients are based on a special type
of singular element decomposition. We show that this decomposition can be
used to construct the parabolic Verma modules and finally to obtain the
generalized Weyl-Verma formulas for characters. We demonstrate how branching coefficients can determine the generalized BGG resolution sequence.
\end{abstract}

@@

The resolution of irreducible modules in terms of infinite-dimensional ones is important for the
theory of integrable spin chains \cite{derk1008}. In the Baxter $\mathcal{Q}$-operator approach \cite{derk09} the generic transfer
matrices corresponding to the (generalized) Verma modules are factorized into the product of Baxter
operators. The resolution allows to calculate the transfer matrices for finite-dimensional
auxiliary spaces.

To show the connection of the BGG resolution with the branching we use the recursive approach presented in \cite
{2010arXiv1007.0318L} (similar to the one used in \cite{ilyin812pbc} for
maximal embeddings). We consider the subalgebra $\af \hookrightarrow \gf$ together with its
counterpart $\afb$ ''orthogonal'' to $\af$ with respect to
the Killing form and also $\widetilde{\afb}:=\afb\oplus \frak{h}_{\perp }$ where $\frak{h}=\frak{\frak{h}_{\af}}\oplus
\frak{h}_{\afb}\oplus \frak{h}_{\perp }$. For any reductive
subalgebra $\af$ the subalgebra $\afb\hookrightarrow \gf$
is regular and reductive. For a highest weight integrable module $%
L^{\left(\mu \right) }$ and orthogonal subalgebra $\af_{\bot }$ we
consider the singular element $\Psi ^{\left( \mu \right) }$ (the numerator
in the Weyl character formula $ch\left( L^{\mu }\right) =\frac{\Psi ^{\left(
\mu \right) }}{\Psi ^{\left( 0\right) }}$, see for example \cite
{humphreys1997introduction}) and the Weyl denominator $\Psi _{\af_{\bot
}}^{\left( 0\right) }$ for the orthogonal partner. It is shown that the element $\Psi _{\gf%
}^{\left( \mu \right) }$ can be decomposed into a combination of Weyl
numerators $\Psi _{\af_{\bot }}^{\left( \nu \right) }$ with $\nu \in P_{%
\mathfrak{a}_{\bot}}^{+}$. This decomposition provides the possibility to
construct the set of highest weight modules $L_{\afb}%
^{\mu _{\afb}}$. When the injection \ $\af%
_{\bot }\hookrightarrow \gf$ \ satisfies the ''standard parabolic''
conditions these modules give rise to the parabolic Verma modules $M_{\left(
\afb \hookrightarrow \gf\right) }^{\mu _{%
\afb}}$ so that the initial character $ch\left(
L^{\mu }\right) $ is finally decomposed into the alternating sum of such. On
the other hand when the parabolic conditions are violated the construction
survives and exhibits a decomposition with respect to a set of generalized Verma
modules $M_{\left( \widetilde{\frak{b}_{\perp }},\gf\right) }^{\mu _{%
\widetilde{\afb}}}$ where $%
\widetilde{\frak{b}_{\perp }}$ is not a subalgebra in $\gf$ but a
contraction of $\widetilde{\afb}$.

Some general properties of the proposed decompositions are formulated in
terms of a specific formal element $\Gamma _{\af\rightarrow \gf}$  called ''the injection fan''. Using this tool a simple and explicit algorithm for branching
rules applicable for an arbitrary (maximal or
nonmaximal) subalgebra in affine Lie algebras was
proposed in \cite{2010arXiv1007.0318L}.

Possible further developments are discussed in Section \ref{sec:conclusions}.

@@

Consider Lie algebras (affine Lie algebras) $\frak{g}$ and $\frak{a}$ and an
injection $\frak{a}\hookrightarrow \frak{g}$ such that $\frak{a}$ is a
reductive subalgebra $\frak{a\subset g}$ with correlated root spaces: $\frak{%
h}_{\frak{a}}^{\ast }\subset \frak{h}_{\frak{g}}^{\ast }$. We use the
following notations:

$\frak{g=n}^{-}+\frak{h}+\frak{n}^{+}$ --- the Cartan decomposition;

$r$ , $\left( r_{\frak{a}}\right) $ --- the rank of the algebra $\frak{g}$ $%
\left( \mathrm{{resp. }\frak{a}}\right) $ ;

$\Delta $ $\left( \Delta _{\frak{a}}\right) $--- the root system; $\Delta
^{+} $ $\left( \mathrm{{resp. }\Delta _{\frak{a}}^{+}}\right) $--- the
positive root system (of $\frak{g}$ and $\frak{a}$ respectively);

$\mathrm{mult}\left( \alpha \right) $ $\left( \mathrm{mult}_{\frak{a}}\left(
\alpha \right) \right) $ --- the multiplicity of the root $\alpha$ in $%
\Delta $ (resp. in $\left( \Delta _{\frak{a}}\right) $);

$S\quad \left( S_{\frak{a}}\right) $ --- the set of simple roots (for
$\gf$ and $\af$ respectively);

$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
i$-th (resp. $j$-th) simple root for $\frak{g}$ $\left( \mathrm{{resp.}\frak{a%
}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;

$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
}\right) $-- the simple coroot for $\frak{g}$ $\left( \mathrm{{resp.}\frak{a}%
}\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;

$W$ , $\left( W_{\frak{a}}\right) $--- the Weyl group;

$C$ , $\left( C_{\frak{a}}\right) $--- the fundamental Weyl chamber;

$\bar{C}, \left(\bar{C_{\frak{a}}}\right)$ --- the closure of the
fundamental Weyl chamber;

@@

$\rho $\ , $\left( \rho _{\frak{a}}\right) $\ --- the Weyl vector;

$L^{\mu }$\ $\left( L_{\frak{a}}^{\nu }\right) $\ --- the integrable module
of $\frak{g}$ with the highest weight $\mu $\ ; (resp. integrable $\af$-module
with the highest weight $\nu $);

$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
the weight diagram of $L^{\mu }$ (resp. ${}L_{\frak{a}}^{\nu }$ );

$P$ (resp. $P_{\frak{a}} $) \ --- the weight lattice;

$P^{+}$ (resp. $P_{\frak{a}}^{+} $) \ --- the dominant weight lattice;

$m_{\xi }^{\left( \mu \right) }$ , $\left( m_{\zeta }^{\left( \nu \right)
}\right) $ --- the multiplicity of the weight $\xi \in P$ \ $\left( \mathrm{{%
resp. }\in P_{\frak{a}}}\right) $ in $L^{\mu }$, (resp. in $\zeta \in
L_{\frak{a}}^{\nu } $);

$ch\left( L^{\mu }\right) $ (resp. $\mathrm{ch}\left( L_{\frak{a}}^{\nu
}\right) $)--- the formal character of $L^{\mu }$ (resp. of $L_{\frak{a}}^{\nu
} $);

@@

$R:=\prod_{\alpha \in \Delta ^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{{%
mult}\left( \alpha \right) }}\quad $ (resp. $R_{\frak{a}}:=\prod_{\alpha \in
\Delta _{\frak{a}}^{+}}\left( 1-e^{-\alpha }\right) ^{\mathrm{mult}_{\frak{a}%
}\left( \alpha \right) } $)--- the Weyl denominator.

\section{Orthogonal subalgebra and\\ singular elements}

@@

In this section we shall show how the recurrent approach to branching
problem leads naturally to a presentation of a formal character of
$\frak{g}$-module in terms characters corresponding to a set
of parabolic (generalized) Verma modules. Consider a reductive
Lie algebra $\frak{g}$ and its reductive subalgebra $\frak{a}\subset \frak{g}$.
Let $L^{\mu} $ be the highest weight integrable module of $\frak{g}$, $\mu \in
P^{+}$. Let $L^{\mu }$ be completely reducible with respect to $\frak{a}$,
\begin{equation*}
L_{\frak{g}\downarrow \frak{a}}^{\mu }=\bigoplus\limits_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{\left( \mu \right) }L_{\frak{a}}^{\nu }.
\end{equation*}
Using the projection operator $\pi _{\frak{a}}$ (to the weight space $\frak{%
h_{a}}^{\ast }$) one can write this decomposition in terms of formal
characters:
\begin{equation}
\pi _{\frak{a}}ch\left( L^{\mu }\right) =\sum_{\nu \in P_{\frak{a}%
}^{+}}b_{\nu }^{(\mu )}ch\left( L_{\frak{a}}^{\nu }\right) .
\label{branching1}
\end{equation}
The module $L^{\mu }$ has the BGG resolution (see \cite
{bernstein1976category,bernstein1975differential,bernstein1971structure} and
\cite{humphreys2008representations}). All the members of the filtration
sequence are the direct sums of Verma modules and all their highest weights $%
\nu $ are strongly linked to $\mu $:
\begin{equation*}
\left\{ \nu \right\} =\left\{ w\left( \mu +\rho \right) -\rho |w\in
W\right\} .
\end{equation*}

@@

Let $\frak{h}_{\frak{a}}$ be a Cartan subalgebra of $\mathfrak{g}$. For $%
\mathfrak{a}\hookrightarrow \frak{g}$ introduce the ''orthogonal partner'' $%
\mathfrak{a}_{\bot }\hookrightarrow \frak{g}$ .

Consider the root subspace $\frak{h}_{\perp \frak{a}}^{\ast }$ orthogonal to
$\frak{a}$,
\begin{equation*}
\frak{h}_{\perp \frak{a}}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
h\in \frak{h}_{\frak{a}};\eta \left( h\right) =0\right\} ,
\end{equation*}
and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
to $\frak{a}$,
\begin{eqnarray}
\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} ,
\label{delta a ort} \\
\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
}^{+}|\forall h\in \frak{h}_{\frak{a}};\beta ^{+}\left( h\right) =0\right\} .
\notag
\end{eqnarray}
Let $W_{\frak{a}_{\perp }}$ be the subgroup of $W$ generated by the
reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\frak{a}_{\perp
}}^{+}$. The subsystem $\Delta _{\frak{a}_{\perp }}$ determines the
subalgebra $\frak{a}_{\perp }$ with the Cartan subalgebra $\frak{h}_{\frak{a}%
_{\perp }}$. Let
\begin{equation*}
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
}|\forall h\in \frak{h}_{\frak{a}\oplus \frak{a}_{\perp }};\eta \left(
h\right) =0\right\}
\end{equation*}
so that $\frak{g}$ has the subalgebras
\begin{eqnarray}
\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
\qquad
\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }.
\end{eqnarray}
Notice that $\mathfrak{a} \oplus \mathfrak{a}_{\bot}$ in general is not a
subalgebra in $\mathfrak{g}$.

For the Cartan subalgebras we have the decomposition
\begin{equation}
\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus
\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus \frak{h}_{%
\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}\oplus
\frak{h}_{\frak{a}}.
\end{equation}
For $\frak{a}$ and $\frak{a}_{\perp }$ consider the
corresponding Weyl vectors, $\rho _{\frak{a}}$ and $\rho _{\frak{a}_{\perp
}} $. Form the so called ''defects'' $\mathcal{D}_{\frak{a}}$ and $\mathcal{%
D}_{\frak{a}_{\perp }}$ of the injection:
\begin{equation}
\mathcal{D}_{\frak{a}}:=\rho _{\frak{a}}-\pi _{\frak{a}}\rho , \qquad
\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
_{\perp }}\rho .  \label{defect ort}
\end{equation}

For $\mu \in P^{+}$ consider the linked weights $\left\{
\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $. Consider the projections to
$h_{\frak{a}_{\perp }}^{\ast }$ additionally shifted by the defect $-%
\mathcal{D}_{\frak{a}_{\perp }}$:
\begin{equation*}
\mu _{\frak{a}_{\perp }}\left( w\right) :=\pi _{\frak{a}_{\perp }}\left[
w(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad w\in W.
\end{equation*}
Among the weights $\left\{ \mu _{\frak{a}_{\perp
}}\left( w\right) |w\in W\right\} $ one can always choose those located in
the fundamental chamber $\overline{C_{\frak{a}_{\perp }}}$. Let $U$ be the
set of representatives $u$ for the classes $W/W_{\frak{a}_{\perp }}$ such
that

\begin{equation}
U:=\left\{ u\in W|\quad \mu _{\frak{a}_{\perp }}\left( u\right) \in
\overline{C_{\frak{a}_{\perp }}}\right\} \quad .  \label{U-def}
\end{equation}
Thus we can form the subsets:
\begin{equation}
\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}%
_{\perp }},\quad u\in U,  \label{mu-a}
\end{equation}
and
\begin{equation}
\mu _{\frak{a}_{\perp }}\left( u\right) :=\pi _{\frak{a}_{\perp }}\left[
u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }},\quad u\in U.
\label{mu-a-tilda}
\end{equation}

Notice that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
since it is built on a subset of roots of the algebra $\mathfrak{g}$.

For the modules we are interested in the Weyl-Kac formula for $\mathrm{ch}%
\left( L^{\mu }\right) $ can be written in terms of singular elements \cite
{humphreys1997introduction},
\begin{equation*}
\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w(\mu +\rho
)-\rho },
\end{equation*}
namely,
\begin{equation}
\mathrm{ch}\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi
^{\left( 0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.
\label{Weyl-Kac2}
\end{equation}
The same is true for the submodules $\mathrm{ch}\left( L_{\frak{a}}^{\nu
}\right) $ in (\ref{branching1})
\begin{equation*}
\mathrm{ch}\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left(
\nu \right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
}^{\left( \nu \right) }}{R_{\frak{a}}},
\end{equation*}
with
\begin{equation*}
\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
}}\epsilon (w)e^{w(\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}.
\end{equation*}
